Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
Clarify that much of the software in the papers examined was FOSS

Much of the software used are Free open-source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
MEGA was the most widely cited software in this evaluation reflecting the widespread use of sequence analysis in the field of plant pathology.
The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
It is interesting to note however, that even with the popularity of Python in scientific programming it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.

>>>>

Much of the software that was used in the papers examined were Free Open-Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
MEGA was the most widely cited software in this evaluation reflecting the widespread use of sequence analysis in the field of plant pathology.
The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
It is interesting to note however, that even with the popularity of Python in scientific programming it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.
